\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-05-01 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

>>>>

You can add -DFORCE\_VECTORIZATION to the compiler options in \texttt{flags.guess} (for all compilers, except for IBM for which the syntax is -WF,-DFORCE\_VECTORIZATION )
to speed up the code in the fluid (acoustic) parts (only; FORCE\_VECTORIZATION support for elastic parts has been discontinued in the source code).
This works fine if (and only if) your computer always allocates a contiguous memory block for each allocatable array;
this is the case for most machines and most compilers, but not all. For more details see https://github.com/geodynamics/specfem3d/issues/81 .
To check if that option works fine on your machine, run the code with and without it for a model containing a significant fluid layer
(or entirely fluid) and make sure the seismograms are identical.\\
